Examining FDR correction issue in clusterProfiler - RNA-seq example

### 2024-07-09 analysis/analyse_rnaseq2.Rmd
pdf2

@@

png("fig2_ORAsz.png")

dev.off()

>>>>

pdf("fig2_ORAfdr.pdf",width=7,height=7)
par(mar=c(c(5.1, 7.1, 2.1, 2.1) ))
barplot(t(df),beside=TRUE,horiz=TRUE,las=1,xlim=c(0,330),
  xlab="no. significant sets",
  col=c("gray30","gray80"))
text(df$ns1+20,((1:nrow(df))*3)-1.5,labels=signif(df[,1],3))
text(df$ns2+20,((1:nrow(df))*3)-0.5,labels=signif(df[,2],3))
legend("bottomright", inset=.02, legend=c("corrected","original"),
  fill=c("gray80","gray30"), horiz=FALSE, cex=1)
dev.off()

@@

png("fig2_ORAsz.png")
plot(jac[,"GO"],type="b", pch=19,cex=1.5,lwd=2,
  xaxt = "n",ylim=c(0,1),ylab="Jaccard index",xlab="no. genes selected")
axis(1, at = seq(1, 5, by = 1),
     labels = ngenes)
points(jac[,"Reactome"],type="b",col="red",pch=19,cex=1.5,lwd=2)
points(jac[,"Cellmarkers"],type="b",col="blue",pch=19,cex=1.5,lwd=2)
points(jac[,"TFT GTRD"],type="b",col="gray50",pch=19,cex=1.5,lwd=2)

legend("bottomright", legend=c("GO","Reactome", "Cellmarkers", "TFT"),
       col=c("black", "red", "blue", "gray50"), lty=1, cex=1.2,lwd=3,pch=19)
dev.off()

pdf("fig2_ORAsz.pdf",width=7, height=7)
plot(jac[,"GO"],type="b", pch=19,cex=1.5,lwd=2,
  xaxt = "n",ylim=c(0,1),ylab="Jaccard index",xlab="no. genes selected")
axis(1, at = seq(1, 5, by = 1),
     labels = ngenes)
points(jac[,"Reactome"],type="b",col="red",pch=19,cex=1.5,lwd=2)
points(jac[,"Cellmarkers"],type="b",col="blue",pch=19,cex=1.5,lwd=2)
points(jac[,"TFT GTRD"],type="b",col="gray50",pch=19,cex=1.5,lwd=2)

legend("bottomright", legend=c("GO","Reactome", "Cellmarkers", "TFT"),
       col=c("black", "red", "blue", "gray50"), lty=1, cex=1.2,lwd=3,pch=19)
dev.off()
